---
title: "flightsim_survey_pgm"
date: "`r Sys.Date()`"
output:
    html_document:
      theme: cosmo
      df_print: paged 
      number_sections: yes
---
--------------------------------------------------------------------------------

# Documentation Block

--------------------------------------------------------------------------------


**PURPOSE**
- This program is used to process and analyze data used in the research report
**SELECTS**
- This program uses two data sources: A set of web-scraped product reviews and survey data to flight simulation enthusiasts
**NOTES**
-
**DATA REQUIRED**
```{r echo=FALSE, message=FALSE, warning=FALSE, results="show"}

# ---------------------- DEPENDENCIES ----------------------------------

library(tidyverse) # dplyr/data processing 
library(janitor) # clean variable names/data processing
library(readxl) # read excel files
library(ggplot2) # for graphing
library(gridExtra) # Arranging Plots
library(grid) # Arranging Plots
library(svglite) # Saving SVG files
library(flextable) # for tabling
library(tools) # for graphing aesthetics

# ---------------------- R ENVIORNMENT ----------------------------------

# Turn off scientific notation
options(scipen = 999)

# Suppress display of Rmd chunk code by default
knitr::opts_chunk$set(echo=FALSE)

# Create program metadata variables
filpath <- rstudioapi::getActiveDocumentContext()$path # File Path 
prgname <- str_sub(str_extract(filpath, "[^/]*$"), end = 5) # Program Name
prgdate <- format(Sys.Date(), '%y%m%d') # Program Date

# ---------------------- DATA FILES AND DIRECTORIES ----------------------------------

# Input Directories
usedir1 <- "~/Desktop/Flightsim/survey/"
usedir2 <- "~/Desktop/Flightsim/survey/review_data"

# Input Files
usefil1 <- "flightsim_survey_rawdata.csv" # Survey Data
usefil2 <- "velocityone_class60524.xlsx" # Turtle Beach Review Data 
usefil3 <- "honeycomb_class60524.xlsx" # Honey Comb Review Data 
usefil4 <- "thrustmaster_class60524.xlsx" # Thrustmaster Boeing Review Data 

# Output Directories
savdir1 <- getwd()

# Output Files
savfil1 <- "donut_chart_ar.svg"
savfil2 <- "donut_chart_s.svg"
savfil3 <- "bar_chart_afr.svg"
savfil4 <- "bar_chart_cmr.svg"

```

--------------------------------------------------------------------------------

# Read in files

--------------------------------------------------------------------------------


### Survey Data

```{r}
# Import survey data
survey_rawdata <- read_csv(file.path(usedir1, usefil1))

# Inspect/preview data
head(survey_rawdata)
```


### Customer Reviews

**Turtle Beach**
```{r}
# Import Product Reviews
prod_reviews_tb_rawdata <- read_xlsx(file.path(usedir2, usefil2))

# Inspect/preview data
head(prod_reviews_tb_rawdata)
```

**Honeycomb**
```{r}
prod_reviews_hc_rawdata <- read_xlsx(file.path(usedir2, usefil3))

head(prod_reviews_hc_rawdata)
```

**Thrustmaster**
```{r}
prod_reviews_tmb_rawdata <- read_xlsx(file.path(usedir2, usefil4))

head(prod_reviews_tb_rawdata)
```


--------------------------------------------------------------------------------

# Data Processing

--------------------------------------------------------------------------------


### Customer Reviews 

**Yoke Smoothness**
Clean and and prepare qualitative coding results for negative reviews (3 stars or lower) with negative sentiment toward Yoke Smoothness. For more information on the coding criteria of yoke smoothness and qualitative process, see *LINK*

```{r}
# Turtle Beach------------------------------------------------------------------
table(prod_reviews_tb_rawdata$yokesmooth_class_result2) # view raw coding results

turtlebeach_reviewdata <- prod_reviews_tb_rawdata %>% 
  clean_names() %>% # clean variable names
  mutate(yokesmooth_class_result2 = case_when( 
    yokesmooth_class_result2 %in% c("No", "No.") ~ "No", # Change "No." to "No"
    yokesmooth_class_result2 %in% c("Yes", "Yes.") ~ "Yes" # Change "Yes." to "Yes"
  ))

table(turtlebeach_reviewdata$yokesmooth_class_result2)  # Check

```

```{r}
# Honeycomb---------------------------------------------------------------------
table(prod_reviews_hc_rawdata$yksmooth_class_result...10) # view raw coding results

honeycomb_reviewdata <- prod_reviews_hc_rawdata %>%
  mutate(yksmooth_class_result...10 = case_when(
    yksmooth_class_result...10 %in% c("No", "No.") ~ "No", # Change "No." to "No"
    yksmooth_class_result...10 %in% c("Yes", "Yes.") ~ "Yes" # Change "Yes." to "Yes"
  )) %>% 
  clean_names() # clean variable names

table(honeycomb_reviewdata$yksmooth_class_result_10) # Check

```

```{r}
# Thrustmaster------------------------------------------------------------------
table(prod_reviews_tmb_rawdata$yksmooth_class_result_r) # view raw coding results

thrustmaster_reviewdata <- prod_reviews_tmb_rawdata %>% 
  clean_names() %>% # clean variable names
  mutate(yksmooth_class_result_r = case_when(
    yksmooth_class_result_r %in% c("No", "No.") ~ "No", # Change "No." to "No" 
    yksmooth_class_result_r %in% c("Yes", "Yes.") ~ "Yes" # Change "Yes." to "Yes"
  ))

table(thrustmaster_reviewdata$yksmooth_class_result_r) # Check

```


```{r}
# Clean environment

rm(prod_reviews_hc_rawdata, prod_reviews_tb_rawdata, prod_reviews_tmb_rawdata)
```


### Survey

**Clean Variable Names**
Rename question 2 and 3 columns so that they contain the feature/yoke in the suffix 
of each column name

```{r}
# Question 2 -------------------------------------------------------------------
# : When purchasing a flight simulator yoke, rank the following features and 
# : capabilities from most important (1)  to least important (12). Drag and drop to rank the yokes.
#  -----------------------------------------------------------------------------

# Create temporary variable
tmp <- survey_rawdata

# Specify the columns to rename
columns_to_rename <- survey_rawdata %>% select(starts_with("Q2_")) %>% names()

# Extract parts after "-" from the first row for the specified columns
suffixes <- sapply(tmp[1, columns_to_rename], function(x) sub(".*-", "", x))

# Get current column names
current_names <- colnames(tmp)

# Create new names for the specified columns
new_names <- paste(columns_to_rename, suffixes, sep = "_")

# Rename the specified columns
colnames(tmp)[colnames(tmp) %in% columns_to_rename] <- new_names

# Clean names
tmp2 <- tmp %>% clean_names() 

# Remove temporary variables
rm(tmp, columns_to_rename, suffixes, current_names, new_names) 
```

```{r}
# Question 3 -------------------------------------------------------------------
# : Imagine you are looking to purchase a flight simulator yoke and are 
# : considering Yoke A, Yoke B, and Yoke C. The features of the three yokes are 
# : listed in the tables below. Please rank #the following yokes from most 
# : desirable (1) to least desirable (3), assuming that each yoke costs $400. 
# : Drag and drop to rank the yokes.
#  -----------------------------------------------------------------------------

# Create temporary variable
tmp <- tmp2

# Specify the columns to rename
columns_to_rename <- tmp %>% select(starts_with("q3_")) %>% names()

# Extract parts after "-" from the first row for the specified columns
suffixes <- sapply(tmp[1, columns_to_rename], function(x) sub(".*-", "", x))

# Get current column names
current_names <- colnames(tmp)

# Create new names for the specified columns
new_names <- paste(columns_to_rename, suffixes, sep = "_")

# Rename the specified columns
colnames(tmp)[colnames(tmp) %in% columns_to_rename] <- new_names

# Create temporary variables
tmp3 <- tmp

# Remove temporary variables
rm(tmp, tmp2, columns_to_rename, suffixes, current_names, new_names) # Remove temporary variables
```


**Apply Survey Filters**

Remove responses from:
 1. Survey Preview Responses
 2. Respondents who do not own a flight simulation yoke
 3. Respondents who only have HOTAS style controllers
 4. Remove respondents who quit survey after question 1
 5. Remove respondents with inconsistent location responses (Falsely claimed to live in the SF Bay Area)

```{r}
# Prepare for filtering based on location (filter 5)---------------------------------------
# We remove all responses who claimed to live in the SF bay area but coordinates 
# reported by Qualtrics were outside a 100 mile radius of San Ramon, CA.  

## Function to calculate haversine distance
haversine_distance <- function(lat1, lon1, lat2, lon2) {
  R <- 3959  # Earth radius in miles
  dLat <- (lat2 - lat1) * pi / 180
  dLon <- (lon2 - lon1) * pi / 180
  lat1 <- lat1 * pi / 180
  lat2 <- lat2 * pi / 180
  a <- sin(dLat/2) * sin(dLat/2) + sin(dLon/2) * sin(dLon/2) * cos(lat1) * cos(lat2)
  c <- 2 * atan2(sqrt(a), sqrt(1 - a))
  d <- R * c
  return(d)
}

## San Ramon, CA coordinates
san_ramon_lat <- 37.7799
san_ramon_lon <- -121.978

```

```{r}
# Prepare to filter to include only owners of Yoke style controllers -----------

# Find unique list of text entry HOTAS style controller names that respondents provided
unique(survey_rawdata$Q1_4_TEXT) # Run and filter manually to populate "sticks" object

# Gather responses with flight sticks
sticks <- c("Thrustmaster Warthog", 
           "Thrustmaster TCA Sidestick", 
           "Thrustmaster TCA Airbus", 
           "Thrustmaster Hotas Warthog", 
           "Sidewinder Force Feedback 2", 
           "Logitech x52 hotas", 
           "Logitech extreme 3d pro (I’m cheap)", 
           "Have HOTAS")

# Assign names to filter object
exc_filter <- paste(sticks, collapse = "|")

```

```{r}
# Create dummy variables for filters -------------------------------------------

tmp4 <- tmp3 %>%
  # Remove header rows
  slice(-(1:2)) %>%  
  # Create dummies
  mutate(
    ## Track pre-filtered rows
    initial_sample = 1,  
    ## If survey previews (filter 1)
    survey_preview = ifelse(status == "Survey Preview", 1, 0),  
    ## If no yoke ownership (filter 2)
    no_yoke = ifelse(grepl("I do not own a flight simulation yoke", q1, ignore.case = TRUE), 1, 0),  
    ## If only own HOTAS yokes (filter 3)
    hotas = ifelse(q1 == "Other" & grepl(exc_filter, q1_4_text, ignore.case = TRUE), 1, 0)  
  ) %>%
  rowwise() %>%
  mutate(
    # If quit after Q1 (filter 4)
    quit_aq1 = ifelse(all(is.na(c_across(q2_1_xbox_compatibility:q15))), 1, 0)  
  ) %>%
  ungroup() %>%
  mutate(
    location_latitude2 = as.numeric(location_latitude), # Make coordinates numeric
    location_longitude2 = as.numeric(location_longitude),
    # Calculate distance from San Ramon
    distance_to_sr = haversine_distance(location_latitude2, location_longitude2, 
                                        san_ramon_lat, san_ramon_lon),
    # If within 100 miles of San Ramon
    radius100 = ifelse(distance_to_sr <= 100, TRUE, FALSE),  
    # Claimed Bay Area but outside 100 miles (filter 5)
    inbay_ovr100 = ifelse(radius100 == FALSE & q12 == "Yes", TRUE, FALSE)  
  )

```

```{r}
# Filter data ------------------------------------------------------------------

# Apply the filters to get the final analysis sample
tmp5 <- tmp4 %>%
  mutate(ansamp = ifelse( # change this mutate and have this define the ansamp == 1
    survey_preview == 0 & # (1) Remove survey previews 
    no_yoke == 0 & # (2) Remove respondents who don't have a yoke
    hotas == 0 &  # (3) Remove respondents who only have HOTAS controllers
    quit_aq1 == 0 & # (4) Remove respondents who quit survey after Q1
    inbay_ovr100 == FALSE, 1, 0)) # (5) Remove respondents with inconsistent location responses

# Create final data for analysis  
data <- tmp5 %>% 
  select(-survey_preview, -no_yoke, -hotas, -quit_aq1) %>% # remove filter variables
  filter(ansamp == 1) # filter to include analysis sample only

```


**Check Number of Rows Removed**
```{r}
# OLD 
paste0("Old N: ", nrow(tmp4))

# NEW
paste0("New N: ", nrow(data))

```

```{r}
# Spot check removed rows 
removed_rows <- tmp5 %>% filter(ansamp == 0)

# Table filters
tmp5 %>% select(survey_preview,
                no_yoke,
                hotas,
                quit_aq1,
                inbay_ovr100, 
                ansamp) %>% 
  group_by_all() %>% 
  summarise(N = n(), .groups = "drop") %>% 
  flextable() %>% 
  autofit()
```


**Check Filtered**
```{r}
# (1) Survey previews and (2) yoke ownership
data %>% select(status, q1) %>% 
  group_by_all() %>% 
  summarise(N = n(), .groups = "drop") %>% 
  flextable() %>% # create table
  autofit()

```

```{r}
# (3) No hotas ownership 
table(data$q1_4_text)

```

```{r}
# (4) Respondents quitting after Q1
data %>% filter(if_all(q2_1_xbox_compatibility:q15, is.na))

# (5) Inconsistent location responses
locfilter_check <- data %>% 
  select(q12, ends_with("e2"), ends_with("100"), distance_to_sr, ansamp) %>% 
  filter(q12 == "Yes")
```


```{r}
# Clean environment
rm(tmp3, tmp4, tmp5, locfilter_check, removed_rows)
rm(exc_filter, san_ramon_lat, san_ramon_lon, sticks, haversine_distance)
```


--------------------------------------------------------------------------------

# Analysis

--------------------------------------------------------------------------------


### Product Reviews 

Qualitative Analysis Results
- % of reviews (3 stars or lower) that mention yoke smoothness and related problems as an issue.
```{r}
# Turtle beach
addmargins(table(turtlebeach_reviewdata$yokesmooth_class_result2))

# Save proportion for later graphing
tb_review_prop <- round(mean(turtlebeach_reviewdata$yokesmooth_class_result2 == "Yes"), 2)
tb_review_prop 
```

```{r}
# Honeycomb
addmargins(table(honeycomb_reviewdata$yksmooth_class_result_10))

# Save proportion for later graphing
hc_review_prop <- round(mean(honeycomb_reviewdata$yksmooth_class_result_10 == "Yes"), 2)
hc_review_prop 
```

```{r}
# Thrustmaster
addmargins(table(thrustmaster_reviewdata$yksmooth_class_result_r))

# Save proportion for later graphing
tmb_review_prop <- round(mean(thrustmaster_reviewdata$yksmooth_class_result_r == "Yes"), 2)
tmb_review_prop
```


**Donut Chart (Product Reviews)**
```{r}
# Prepare data: proportions of responses for 3 sets of responses
ggdonut_pr_data <- data.frame(
  Category = rep(c("turtle beach", "honeycomb", "thrustmaster"), each = 2),  # 3 categories of responses
  Response = rep(c("Yes", "No"), times = 3),  # Single question, 2 possible answers (Yes/No)
  Proportion = c(tb_review_prop, (1-tb_review_prop),   # Proportions for turtle beach
                 hc_review_prop, (1-hc_review_prop),   # Proportions for honeycomb
                 tmb_review_prop, (1-tmb_review_prop))  # Proportions for thrustmaster
)

# Function to create a single-level donut chart with middle label
create_donut_chart <- function(df, label) {
  ggplot(df, aes(x = 2, y = Proportion, fill = Response)) +
    geom_bar(stat = "identity", width = 0.8, color = "white") +  # Single donut
    coord_polar(theta = "y") +
    theme_void() +  # Remove axis and background
    xlim(0.5, 2.5) +  # Adjust the limit to create the hole
    geom_text(aes(label = ifelse(Response == "Yes", scales::percent(Proportion), "")),
              position = position_stack(vjust = 0.5), color = "black") +  # Percentage labels in black
    annotate("text", x = 0.5, y = 0, label = label, size = 4, color = "black") +  # Center label in black
    theme(legend.position = "none")  # Remove the legend
}

# Prepare graphs for the three categories
donut1 <- create_donut_chart(filter(ggdonut_pr_data, Category == "turtle beach"), "Turtle Beach")
donut2 <- create_donut_chart(filter(ggdonut_pr_data, Category == "honeycomb"), "Honeycomb")
donut3 <- create_donut_chart(filter(ggdonut_pr_data, Category == "thrustmaster"), "Thrustmaster")

# Arrange the three charts horizontally
gd_pr <- arrangeGrob(donut1, donut2, donut3, ncol = 3)

# Add a main title with adjusted positioning
grid.newpage()  # Clear the current page
grid.rect(gp = gpar(fill = "white", col = NA))  # Set background color behind all charts
grid.text("Product Reviews:\nPercentage of reviews (3 stars or lower) that mention pitch smoothness\nand related features as an issue", x = 0.5, y = 0.85, gp = gpar(fontsize = 11, fontface = "bold"))  # Adjust title position

grid.draw(gd_pr)  # Draw the grob

# Preview
gd_pr

```


```{r}
# clean environment 

rm(donut1, donut2, donut3, ggdonut_pr_data, 
   hc_review_prop, tb_review_prop, tmb_review_prop) # clean environment
```


### Survey 

####### **General Yoke Smoothness**

- **Turtle Beach**
```{r}
# Process data
q9_tb_data <- data %>%
  filter(grepl("Turtle Beach Velocity One", q1, ignore.case = TRUE),
         (grepl("Turtle Beach: Velocity One", q9, ignore.case = TRUE) | 
          grepl("not", q9, ignore.case = TRUE)))
         

# Create a frequency table for the column 'q9' in the filtered data
table(q9_tb_data$q9)

# Summarize data
q9_tb_propy <- q9_tb_data %>%
  mutate(q9 = ifelse(grepl(" not ", q9, ignore.case = TRUE), "no", "yes")) %>%
  summarise(yes_p = mean(q9 == "yes"), total_n = n(), yes_n = sum(q9 == "yes"))

q9_tb_propy

```

- **Honeycomb**
```{r}
q9_hc_data <- data %>%
  filter(grepl("Honeycomb", q1, ignore.case = TRUE),
         (grepl("Honeycomb", q9, ignore.case = TRUE) | 
          grepl(" not ", q9, ignore.case = TRUE)))
         

table(q9_hc_data$q9)

q9_hc_propy <- q9_hc_data %>%
  mutate(q9 = ifelse(grepl(" not ", q9, ignore.case = TRUE), "no", "yes")) %>%
  summarise(yes_p = mean(q9 == "yes"), total_n = n(), yes_n = sum(q9 == "yes"))

q9_hc_propy

```

- **Thrustmaster**
```{r}
q9_tmb_data <- data %>%
  filter(grepl("Thrustmaster", q1, ignore.case = TRUE),
         (grepl("Thrustmaster", q9, ignore.case = TRUE) | 
          grepl(" not ", q9, ignore.case = TRUE)))
         

table(q9_tmb_data$q9)

q9_tmb_propy <- q9_tmb_data %>%  
  mutate(q9 = ifelse(grepl(" not ", q9, ignore.case = TRUE), "no", "yes")) %>%
  summarise(yes_p = mean(q9 == "yes"), total_n = n(), yes_n = sum(q9 == "yes"))

q9_tmb_propy
  

```

- **Other**
```{r}
q9_othr_data <- data %>%
  filter(grepl("other", q1, ignore.case = TRUE),
         (grepl("ChoiceTextEntryValue", q9, ignore.case = TRUE) | 
          grepl(" not ", q9, ignore.case = TRUE)))
         

table(q9_othr_data$q9)

q9_othr_propy <- q9_othr_data %>%
  mutate(q9 = ifelse(grepl(" not ", q9, ignore.case = TRUE), "no", "yes")) %>%
  summarise(yes_p = mean(q9 == "yes"), total_n = n(), yes_n = sum(q9 == "yes"))

q9_othr_propy

```

- **Pie Chart (Survey)**
```{r, fig.width=12, fig.height=4}
# Prepare data: Proportions of responses for 4 sets of responses
ggdonut_sq_data <- data.frame(
  Category = rep(c("turtle beach", "honeycomb", "thrustmaster", "other"), each = 2),  # 4 categories of responses
  Response = rep(c("Yes", "No"), times = 4),  # Only the "Yes" responses
  Proportion = c(q9_tb_propy$yes_p, (1-q9_tb_propy$yes_p),   # Proportions for turtle beach
                 q9_hc_propy$yes_p, (1-q9_hc_propy$yes_p),   # Proportions for honeycomb
                 q9_tmb_propy$yes_p, (1-q9_tmb_propy$yes_p),  # Proportions for thrustmaster
                 q9_othr_propy$yes_p, (1-q9_othr_propy$yes_p)) # Proportions for other
)

# Prepare data for the four categories
donut1 <- create_donut_chart(filter(ggdonut_sq_data, Category == "turtle beach"), "Turtle Beach")
donut2 <- create_donut_chart(filter(ggdonut_sq_data, Category == "honeycomb"), "Honeycomb")
donut3 <- create_donut_chart(filter(ggdonut_sq_data, Category == "thrustmaster"), "Thrustmaster")

# Arrange the three charts horizontally
gd_s <- arrangeGrob(donut1, donut2, donut3, ncol = 3)

# Add a main title with adjusted positioning
grid.newpage()  # Clear the current page
grid.draw(gd_s)  # Draw the final grob
grid.text("Survey Question:\nDo you find the smoothness and feel of the pitch axis an issue in your current yoke?\n", 
          x = 0.5, y = 0.85, gp = gpar(fontsize = 11, fontface = "bold"))  # Adjusted title position

grid.draw(gd_s)  # Draw the grob

# Preview
gd_s

```


```{r}
# Clean workspace
rm(q9_hc_data, q9_hc_propy, q9_othr_data, q9_othr_propy, q9_tb_data, q9_tb_propy, q9_tmb_data, q9_tmb_propy,
   ggdonut_sq_data, donut1, donut2, donut3)

```


####### **Average Feature Rank**

```{r}
# Display the modified data frame
avg_rank_data <- data %>%
  select(starts_with("q2"), response_id) %>% 
  mutate_at(vars(starts_with("q2")), as.numeric) # Convert to numeric

avg_rank_calc <- avg_rank_data %>% 
  select(-response_id) %>%
  summarise_all(mean, na.rm = TRUE) %>%  # Calculate the mean rank for each item
  gather(key = "Item", value = "Average_Rank") %>%  # Convert to long format for easier interpretation
  arrange(Average_Rank)  # Sort by average rank

avg_rank_calc # Mean ranking results
```

**Graphing**
```{r, fig.height=8, fig.width=8}
# Process data
avg_rank_calc_gg <- avg_rank_calc %>% 
  mutate(Item = Item %>%
         sub("q2_[0-9]+_", "", .) %>%  # Remove the dynamic prefix
         gsub("_", " ", .) %>%         # Replace underscores with spaces
         toTitleCase(), # Capitalize the first letter of each word
         Average_Rank = round(Average_Rank, 2),
         Item = ifelse(
           Item == "Smoothness Feel and Precision of the Control Axes", "Smoothness, Feel, and\nPrecision of Control Axes", Item),
         Item = ifelse(
           Item == "Included Throttle Control", "Included\nThrottle Control", Item),
         Item = ifelse(
           Item == "Included Rudder Brake Control", "Included Rudder\nBrake Control", Item),
         Item = ifelse(
           Item == "Adequate Resistance Force", "Adequate Resistance\nForce", Item),
         Item = ifelse(
           Item == "Play", "Plug-In-Play", Item)
         )  %>% # Round 
  arrange(desc(Average_Rank)) # Order from lowest to largest average rank           

# Factor
avg_rank_calc_gg$Item <- factor(avg_rank_calc_gg$Item, levels = avg_rank_calc_gg$Item)


# Create a horizontal bar plot with values displayed on the bars
gg_afr <- avg_rank_calc_gg %>% 
  ggplot(aes(x = Average_Rank, y = Item)) +
  
  # Bars
  geom_segment(aes(x=0, xend=Average_Rank, y=Item, yend = Item), lwd=8, color = "#5EC6CC") +
  
  geom_rect(aes(xmin = Average_Rank, xmax = Average_Rank, 
                ymin = as.numeric(Item) - 0.25, ymax = as.numeric(Item) + 0.25)) + 
  
  # Annotation
  geom_text(aes(x= Average_Rank, y=Item, label = paste0("  ", Average_Rank)),
            hjust = 0, size=9/.pt, fontface = "plain", check_overlap = FALSE) +  
  
  scale_y_discrete(
    breaks = unique(avg_rank_calc_gg$Item),
    labels = unique(avg_rank_calc_gg$Item),
    expand = c(0.05, 0)
  ) +
  
  scale_x_continuous(
    limits = c(-0.5, 12),
    expand = c(0,0)
  ) + 
  
  # Titles and theme
  ylab("Feature") +
  xlab("Average Rank") +

  theme_bw() +  # Use a clean theme
  theme(
    # Title
    plot.title = element_text(size=11, color = "#000000", face = "bold", margin = margin(0,0,15,0)),
    
    # Text
    axis.text.x = element_text(size = 9, color = "#000000", face = "bold", margin=margin(0,0,15,0)),
    axis.text.y = element_text(size = 9, color = "#000000", face = "plain", hjust = 0, margin = margin(t=0,r=10,b=0,l=0)),
    axis.title.x = element_text(size = 9, color = "#000000", face = "plain", margin = margin(t=-5,r=0,b=0,l=0)),
    axis.title.y = element_text(size = 9 , color = "#000000", face = "bold", angle = 0, margin = margin(r=-33, b=0, l=0), vjust = 1.02),

    # Gridlines
    panel.grid = element_blank(),
    plot.margin = unit(c(.2,.2,.2,.2),"in")) 


# Preview 
gg_afr


```


####### **Conjoint Analysis Mean Ranking**

```{r}
avg_cjrank_data <- data %>%
  select(starts_with("q3"), response_id) %>% 
  mutate_at(vars(starts_with("q3")), as.numeric) # Convert to numeric

avg_cjrank_calc <- avg_cjrank_data %>% 
  select(-response_id) %>%
  summarise_all(mean, na.rm = TRUE) %>%  # Calculate the mean rank for each item
  gather(key = "Item", value = "Average_Rank") %>%  # Convert to long format for easier interpretation
  arrange(Average_Rank)  # Sort by average rank

avg_cjrank_calc # Mean ranking results
```

**Graphing**
```{r, fig.height= = 8, fig.width=8}
#
avg_cjrank_calc_gg <- avg_cjrank_calc %>% 
  mutate(Item = Item %>%
         sub(".*?(Y)", "\\1", .) %>%  # Remove everything prior to the first "Y"
         gsub("_", " ", .) %>%         # Replace underscores with spaces
         str_to_title(), # Capitalize the first letter of each word
         Average_Rank = round(Average_Rank, 2), # Round
         Item = ifelse(
           Item == "Yoke A", "Yoke A\nVelocity One", Item),
         Item = ifelse(
           Item == "Yoke B", "Yoke B\nHoneycomb XPC", Item),
         Item = ifelse(
           Item == "Yoke C", "Yoke C\nTest Yoke", Item))              


# Create a horizontal bar plot with values displayed on the bars
gg_cmr <- avg_cjrank_calc_gg %>% 
  ggplot(aes(x = Average_Rank, y = Item)) +
  
  # Bars
  geom_segment(aes(x=0, xend=Average_Rank, y=Item, yend = Item), lwd=8, color = "#5EC6CC") +
  
  geom_rect(aes(xmin = Average_Rank, xmax = Average_Rank, 
                ymin = Item, ymax = Item)) + 
  
  # Annotation
  geom_text(aes(x= Average_Rank, y=Item, label = paste0("  ", Average_Rank)),
            hjust = 0, size=9/.pt, fontface = "plain", check_overlap = FALSE) + 
  
  scale_y_discrete(
    breaks = unique(avg_cjrank_calc_gg$Item),
    labels = unique(avg_cjrank_calc_gg$Item),
    expand = c(0.3, 0)
  ) +
  
  scale_x_continuous(
    limits = c(-0.1, 3),
    expand = c(0,0)
  ) + 
  
  # Titles and caption
  ylab("Yoke") +
  xlab("Average Rank") +

  theme_bw() +  # Use a clean theme
  theme(
    # Title
    plot.title = element_text(size=11, color = "#000000", face = "bold", margin = margin(0,0,20,0)),
    
    # Text
    axis.text.x = element_text(size = 9, color = "#000000", face = "bold", margin=margin(0,0,0,0)),
    axis.text.y = element_text(size = 9, color = "#000000", face = "plain", hjust = 0.5, margin = margin(t=,r=10,b=0,l=0)),
    axis.title.x = element_text(size = 9, color = "#000000", face = "plain", margin = margin(t=0,r=0,b=0,l=0)),
    axis.title.y = element_text(size = 9 , color = "#000000", face = "bold", angle = 0, margin = margin(r=-45, b=0, l=0), vjust = 1.04),

    
    # Gridlines
    panel.grid = element_blank(),
    plot.margin = unit(c(.2,.5,.2,.5),"in")) 

# Preview
gg_cmr


```

# Output 

```{r}
# Save files 

## Donut Charts 
ggsave(savfil1, plot = gd_pr, width = 12, height = 4, bg = "white")
ggsave(savfil2, plot = gd_s, width = 12, height = 4, bg = "white")


## Bar Graphs
ggsave(savfil3, plot = gg_afr, width = 8, height = 8)
ggsave(savfil4, plot = gg_cmr, width = 8, height = 4)

```

